Twisted eleven-dimensional supergravity

### 2023-09-20 index 2/intro.tex
index rewrite, intro

\section{Introduction}
Superconformal field theories admit a plethora of exactly computable, protected quantities, giving them a distinguished role in supersymmetric physics. 
Since it is believed that all supersymmetric field theories flow to superconformal fixed points, such quantities provide robust invariants of supersymmetric field theories. 
Examples of such a quantity is the superconformal index, which is a generating function for some collection of $R$-charges of certain BPS local operators. 
Crucial steps towards a more mathematical understanding of superconformal indices were taken in \cite{SWchar}, articulated through the construction of twisting.

Introduced by Witten \cite{WittenTwist} and further developed by Costello \cite{CostelloHol}, twisting refers to a localization, or fixed-point, construction for theories equipped with an action of a supersymmetry algebra. 
Operationally, one modifies the BRST differential of the theory by a nilpotent supercharge---the result is a theory for which the infinitesimal translations in the image of the nilpotent supercharge act homotopically trivially. 
When a twist exists (which is almost always) a supersymmetric field theory admits a so-called minimal twist; the resulting theory is a holomorphic-topological field theory that is holomorphic in the maximal number of spacetime directions.

One of the insights of \cite{SWchar} was that superconformal indices count exactly local operators in the minimal twist---accordingly, we may think of the space of local operators in the minimal twist as categorifying the index.
Moreover, the space of local operators, together with its algebra structure under operator product expansion, is part of the richer structure of a \textit{factorization algebra}.
Whilst the former governs the behavior of observables supported at points, the latter organizes observables that are supported on any open set including for example, non-local operators obtained from local ones via a descent procedure.

A principal goal of the present paper is to initiate the study of the factorization algebras of observables associated to the minimal twists of the six-dimensional~$\cN=(2,0)$ superconformal field theories. The full factorization structure is extremely rich, and in this paper we only discuss a small part of it, namely the costalk at a point as a vector space.
This is otherwise known as the space of local operators at the point. 
However, this information is enough to extract familiar quantities like the superconformal index.

%Moreover, the six dimensional $\cN = (2,0)$ theory plays a distinguished role: many interesting lower dimensional superconformal field theories are obtained from it via dimensional reduction. Accordingly, the desired factorization algebras should serve to organize many of the mathematical structures associated to lower dimensional superconformal field theories.

%and three-dimensional $\cN=8$ superconformal field theories. 
Despite its ubiquity, the six-dimensional~$\cN=(2,0)$ supersymmetric theory is quite elusive---it admits no known Lagrangian formulation, and outside of the abelian case, is not known to admit a field theoretic realization.
In light of this, we propose to access the minimal twist and its local operators via the proposal of \textit{twisted holography}.

\subsection{Our approach via twisted holography}
Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of supersymmetric twists.
Fundamentally, it conjectures a duality between the algebra of observables of a twisted gravitational theory and the algebra of observables of a twisted gauge theory describing the dynamics of a stack of branes coupled to the gravitational theory. There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory sides.

To describe the kinds of theories on either side of the correspondence, we should comment on what it means to twist a theory of supergravity. We will provide more details in \S \ref{s:twisted}. Since the action of supersymmetry is gagued in theories of supergavity, the aforementioned twisting procedure does not quite make sense. Instead, Costello and Li define twisted supergravity to be the theory in perturbation theory around a background where the bosonic ghost for local supertranslations takes a nonzero nilpotent vacuum expectation value. 
Coupling the worldvolume theory of a brane to such a background has the effect of twisting the worldvolume theory in the usual sense.

It is expected that the six-dimensional $\cN=(2,0)$ superconformal field theory of type $A_{N-1}$ describes the low energy dynamics of a stack of fivebranes in M-theory on flat space. Accordingly, there is a minimal twist of the low energy limit of M-theory, eleven-dimensional supergravity, which induces the minimal twist on a stack of fivebranes. We will be interested in a twisted version of the $AdS_{7}/CFT_{6}$ correspondence which will relate the large $N$ limit of the minimally twisted six-dimensional $\cN=(2,0)$ theory with minimally twisted eleven-dimensional supergravity on $AdS_{7}\times S^{4}$.

The twisted holography propoosal moreover posits that holography can be understood as a concrete algebaic operation at the level of observables. We mentioned that the precise mathematical structure modeling observables of a quantum field theory is that of a factorization algebra. The predicted type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.
Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to an (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
Following the work of \cite{CLsugra,CP1} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
If $A$ is the algebra of operators of some bulk quantum field theory (perturbatively we can even consider a theory of gravity) then $A^!$ is the algebra of operators on the universal topological line defect.
Universal here means that algebra of operators on any other line defect which couples to the bulk system admits a unique map of algebras from~$A^!$.

The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so in this paper.
This sort of duality would allow one to make sense of universality statements as above for higher dimensional, possibly non-topological, defects in an arbitrary bulk quantum field theory.
Nevertheless, we can make the following ansatz for the Koszul dual $\cF^!$, which we refer to as the $!$-dual in this paper to avoid confusion, of a factorization algebra~$\cF$ of observables of some bulk quantum field theory.
It is the universal factorization algebra, along a specified defect, which couples to the bulk quantum field theory.
While this heuristic definition sounds natural, it does not lend itself to an explicit description.
However, for particular kinds of factorization algebras of bulk quantum field theories an explicit description is furnished by a local version of Noether's theorem, see~\S\ref{s:noether}.

Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper.
Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory.
Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{N-branes}$.
In the context of branes, it is natural to posit that the universal theory along the brane is given by the large $N$ limit of the factorization algebras $\Obs_{N-branes}$.

Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{N-branes}$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
We can, however, restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.\footnote{In general this is given by some limit construction like for sheaves, but we will use a particularly nice model in the context of holomorphic-topological factorization algebras in this paper.}

\begin{expect}[Twisted holographic principle following \cite{CLsugra}]
After taking into account the backreaction, there is a map of factorization algebras
\[
  (\Obs_{grav}|_{Y})^{!}\to \Obs_{N-branes}
\]
that becomes an equivalence in the large $N$ limit.
\end{expect}

It is natural to wonder how this statement relates to more traditional formulations of the AdS/CFT correspondence, where local operators of the CFT are related to certain states of the gravitational theory on AdS. A precise relation will be articulated in \S\ref{sec:states} where we argue that one can indeed understand $(\Obs_{grav}|_{Y})^{!}$ as a factorization algebra enhancement of the space of (twisted) multi-particle states of the gravitational theory on the backreacted geometry. Explicitly, this geometry refers to the manifold $X - Y$ obtained by subtracting the brane together with the data of a certain Maurer-Cartan element deforming the geometric structure used to define the gravitational theory on $X - Y$.

The above expectation can be tested in instances where both sides of the duality admit explicit descriptions.
This has been carried out in many examples including:
\begin{itemize}
  \item A stack of $D3$ branes in twisted $\Omega$-deformed type IIB supergravity on flat space. The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{costello2021twisted}. This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\cN=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$. Here, the duality is formulated in terms of vertex algebras which are avatars of holomorphic factorization algebras on a Riemann surface.

  \item A system of twisted $D1-D5$ branes in a $T^{4}$-compactification of a twist of type IIB string theory. Upon compactifying along $T^4$ this can be understood as a variant of the above example where the deformed conifold is replaced by a certain superspace \cite{CP}. The duality is understood as a twisted version of the duality between type IIB supergravity on $AdS_{3}\times S^{3}\times T^{4}$ and the symmetric orbifold CFT $Sym^{N}(T^{4})$.

  \item Membranes and fivebranes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}.
In the particular $\Omega$-background, membranes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality. Moreover, the $\Omega$-background localizes fivebranes to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra. The holomorphic factorization algebras we seek in the present paper may be thought of as enhancements of these vertex algebras to three-complex dimensions.
\end{itemize}

In each of the above examples, there exist methods to characterize both sides of the duality independently and intrinsically. Indeed, conjectures of \cite{CLsugra} suggest that certain twists of type II superstrings are equivalent to certain topological strings. Utilizing such a description, one may characterize D-banes and associated open-string field theories in terms of categorical data.

For membranes and fivebranes in $M$-theory, in the nonminimal twist or its further $\Omega$-deformation, one may appeal to dimensional reduction arguments to give similar characterizations of the twisted subsectors of the relevant worldvolume theories.

However, for the minimal twist, we are not so lucky. The dimensional reduction of the nonminimal twist will necessarily involve subtle, nonperturbative effects making an intrinsic characterization along the lines of the above more difficult. We will offer some speculations in this direction at the end of the section below.

Consequentially, rather than prove a version of the twisted holographic principle, the objective of this paper is to \textit{use} the twisted holographic principal to conjecture an explicit description of the factorization algebra associated to the worldvolume theory on a stack of minimally twisted fivebranes. Such an analysis reveals that twists of worldvolume theories of branes enjoy certain infinite dimensional symmetries, enhancing finite dimensional symmetries present in the untwisted theories. In the minimal twist of eleven dimensional supergravity, these infinite dimensional symmetries are provided by certain exceptional simplie lie superalgebras.

\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}

>>>>

\section{Introduction}
Superconformal field theories admit a plethora of protected quantities that can be computed exactly at weak coupling. One such quantity is the superconformal index, which in a Hamiltonian formulation of the theory can be thought of as a Witten-index in radial quantization. Schematically, such a quantity takes the form \[\operatorname{Tr} _{\mc H} \left ( (-1)^F \exp (-\beta \{ Q, \overline Q\} ) x_1^{J_1}\cdots x_n^{J_n}y_1^{H_1}\cdots y_n^{H_n} \right )\] where $(-1)^F$ is the fermion number operator, $\beta$ is an inverse temperature, $Q$ is a supercharge and the $x_i$ are fugacities keeping track of charges under angular momenta, and $y_i$ are fugacities keeping track of charges under R-symmetries. The superconformal index gives a generating function for the difference between bosonic and fermionic states annihilated by a particular supercharge. Under an operator-state correspondence, the superconformal index can also be thought of as a signed count of local operators preserved under a single supercharge.

In terms of partition functions, the superconformal index is gotten by a partition function on a twisted product $M_{1} = S^{1}\times_\omega S^{d-1}$ where the twisting $\omega$ is determined by a background connection for the global symmetries of the problem. Prefactors of exponentiated casimir energies that appear in the partition function are accounted for by central charges which appear in the action of angular momenta on $\mc H$. In superconformal field theories with a holographic dual, one expects a recapitulation of the superconformal index in gravitational terms.

In this article, we revisit the problem of computing the superconformal index of the nebulous six-dimensional superconformal field theory of type $A_{N-1}$ from its holographic dual, eleven-dimensional supergravity on $AdS_7\times S^4$. Recently, we identified a twisted avatar of the $AdS_7\times S^4$ background conjecturally furnished by a $\frac{1}{16}$-BPS field configuration in the physical theory. This background admits an asymptotic symmetry by the infinite dimensional exceptional simple super-Lie algebra $E(3|6)$ and we propose that the full superconformal index ought to be an $E(3|6)$-character.

\parsec[]
Let us recall the interpretation of superconformal indices offered by the AdS/CFT dictionary. traditional formulations of the AdS/CFT correspondence relate two theories, schematically denoted $T_{CFT}$ and $T_{grav}$ on manifolds $M_{1}, M_{2}$ respectively, together with a conformal diffeomorphism $\del M_{2}\cong M_{1}$. The theories have the feature that boundary values of fields of $T_{grav}$ denoted $\phi |_{\del}$, may be identified with sources for $T_{CFT}$ denoted $J$. The two theories are considered to be holographically dual when their partition functions are equivalent $Z_{CFT}[J] = Z_{grav}[\phi |_{\del}]$. In examples of stringy origin, $T_{CFT}$ describes the low energy dynamics of a stack of $N$ branes in supergravity, in the large $N$ limit, and $T_{grav}$ describes gravitational dynamics in the background the branes source. In such examples, the gravitational counterpart of the superconformal index involves summing over geometries which asymptote to $AdS_{d+1} \times K$, where $K$ is compact and the conformal boundary of $AdS_{d+1}$ is identified with $S^1\times_\omega S^{d-1}$. An exciting body of work aims to make this gravitiational incarnation precise, see for example \cite{murthy2020growth} and references therein.

Note that by definition, the superconformal index provides a lower bound on the number of fractionally BPS states of $T_{CFT}$. It is often the case, however, that $T_{grav}$ includes in its spectrum, black holes, which are expected to have a thermodynamic entropy proportional to the event-horizon-area at leading order, as given by the Bekenstein-Hawking formula. As such, the growth of states in $T_{CFT}$, and hopefully the superconformal index, should reflect this.

\parsec[]
Another protected quantity of a superconformal field theory is the algebra of BPS local operators. The vector space underlying this algebra is precisely a costalk of the factorization algebra of observables of a twist. In light of the aforementioned operator-state correspondence, this can be thought of as categorifying the superconformal index. For theories with a holographic dual, local operators of $T_{CFT}$ are supposed to match with certain kinds of states in $T_{grav}$.

Moreover, both kinds of objects transform in representations of a superconformal algebra and the map between them preserves the actions. Local operators in the CFT are equipped with an interesting algebraic structure given by operator-product-expansion, and the AdS/CFT correspondence intertwines this algebraic structure with scattering of supergravity states. Indeed, the equality of partition functions along with the matching of sources for CFT local operators with boundary values of gravitational fields gives a prescription for computing correlation functions between CFT local operators by varying the gravitational action evaluated on field configurations subject to certain boundary values with respect to the boundary value. This recipe can be recast as a tree-level computation in the gravitational theory, involving computation of so-called Witten diagrams.\cite{WittenAdS}.

\subsection{Twisted holography}
Introduced by Costello and Li in \cite{CLsugra}, the twisted holography proposal posits an avatar of the AdS/CFT correspondence that holds at the level of factorization algebras associated to supersymmetric twists of $T_{CFT}$ and $T_{grav}$. There is an exciting body of work being developed around this program including tests of this proposal from both the gravitational and gauge theory sides.

\parsec{}
Concretely, the twisted holography proposal suggests that the type of duality between the factorization algebras associated to a gravitational theory and to the worldvolume theory of a number of branes is a general version of \textit{Koszul duality}.

Ordinary Koszul duality for associative algebras (so quantum mechanical systems) associates to an (augmented) algebra $A$ a dual algebra $A^!$ whose appropriate derived category of modules is the same as that of $A$.
Following the work of \cite{CLsugra, Costello_2021, CostelloM2} (see also the review in \cite{PWkoszul}) there is a simple physical interpretation of Koszul duality.
If $A$ is the algebra of operators of some bulk quantum field theory (perturbatively we can even consider a theory of gravity) then $A^!$ is the algebra of operators on the universal topological line defect.
Universal here means that algebra of operators on any other line defect which couples to the bulk system admits a unique map of algebras from~$A^!$.

The general theory of Koszul duality for factorization algebras has not been developed, and we do not do so here, but see \cite{LurieHA} for the case of $\mb E_n$-algebras and  \cite{gui2022quadratic}, \cite{tamarkin2003deformations} for the case of particular kinds of vertex algebras. This sort of duality would allow one to make sense of universality statements as above for higher dimensional, possibly non-topological, defects in an arbitrary bulk quantum field theory. Roughly, one expects the Koszul dual of a factorization algebra to be the factorization algebra corepresenting the functor of looking at solutions to a Maurer-Cartan equation in a tensor product.

\parsec{}
Let us now make a more concrete, yet slightly informal, statement of twisted holography which fits into the approach of this paper. Let $X$ be a smooth manifold, and let $\Obs_{grav}$ denote a factorization algebra on $X$ that we view as the observables of a bulk gravitational theory. Suppose we have, in addition, a stack of $N$ branes, wrapping a closed submanifold $Y\hookrightarrow X$ whose worldvolume theory has a factorization algebra of observables $\Obs_{CFT}^N$.

Note that $\Obs_{grav}$ is a factorization algebra on $X$, while $\Obs_{CFT}^N$ is a factorization algebra on the closed submanifold $Y$ so we cannot yet compare them.
We can, however, attempt to restrict $\Obs_{grav}$ to a factorization algebra just on $Y$, which we denote by $\Obs_{grav}|_Y$.

\begin{expect}[Twisted holographic principle following \cite{CLsugra}]\label{twistedholog}
There is a map of factorization algebras
\[
  (\Obs_{grav}|_{Y})^{!}\to \Obs_{CFT}^N
\]
that becomes an equivalence in the large $N$ limit.
\end{expect}

As we recalled in the previous subsection, traditional formulations of the AdS/CFT correspondence relate local operators of the gauge theory to states of the gravitational theory on AdS. Therefore, a natural desideratum in relating the above to more traditional statements is a precise relation between the source of the above map and gravitational states in $AdS$. Moreover, there is an operational definition of the operator-product-expansion on the costalk of a Koszul dual factorization algebra which realizes the expectation that Koszul duality corepresents the functor taking Maurer-Cartan elements in the tensor product. Another desideratum is to relate the output of this procedure with the scattering product on gravitational states computed by Witten diagrams.

\begin{rmk}
In this context, the definition of Koszul duality involves another ingredient, namely the backreaction of branes wrapping $Y$. This is meant to capture the fact that $(\Obs_{grav}|_Y)$ may not be canonically augmented, but we may try to deform it in a way that kills off the obstruction to being augmented. More precisely, one expects that the correct version of Koszul duality for application in holographic contexts is a version of \textit{curved} Koszul duality for factorization algebras. 
\end{rmk}

\begin{rmk}
For finite $N$, this map will in general be neither injective nor surjective. The kernel and cokernel of this map for finite $N$ correspond to interesting nonperturbative effects in the gravitational theory. For instance, in gauge theories:

\begin{itemize}
\item This map has a kernel given by trace relations. Syzygies between trace relations are conjecturally related to the worldvolume theories of certain other branes in the gravitational theory, so-called \textit{giant gravitons} \cite{Gaiotto:2021xce}, \cite{choi2023quantum}, \cite{Imamura} \footnote{We thank Ji-Hoon Lee for conversations related to this topic}

\item This map also has a cokernel. By fiat, these are classes that exist in the finite $N$ cohomology of the observables of a gauge theory that are not in the image of the natural map from the large $N$ theory. Recent developments in cohomological approaches to counting quantum microstates of $\frac{1}{16}$-BPS black holes in $AdS_5\times S^5$ \cite{choi2023quantum} \cite{Chang_2023} \cite{Chang_2013} can be cast as trying to characterize the cokernel of a specific example of this map. 
\end{itemize}
\end{rmk}

\parsec[]
The above expectation can be tested in instances where both sides of the duality admit explicit descriptions. This has been carried out in many examples including:
\begin{itemize}
  \item A stack of $D3$ branes in twisted $\Omega$-deformed type IIB supergravity on flat space. The theory on the stack of $D3$ branes is dual to the closed string B-model on the deformed conifold \cite{costello2021twisted}. This can be understood as a twisted $\Omega$-deformed version of the physical AdS/CFT duality between 4d $\mc{N}=4$ super Yang-Mills and type IIB string theory on $AdS_{5}\times S^{5}$. Here the duality can be formulated in terms of vertex algebras.

  \item M2 branes and M5 branes in twisted $\Omega$-deformed $M$-theory on Taub-NUT space \cite{CostelloM5,CostelloM2}. In the particular $\Omega$-background, M2 branes are localized to a topological quantum mechanical system where the duality can be phrased in terms of associative algebras and ordinary Koszul duality. The koszul dual algebra bears close relations to the spherical Cherednik algebra. The $\Omega$-background localizes M5 to a complex plane and the observables of the localized theory are an affine $W_{N}$ vertex algebra. Many celebrated features of the representation theory of these algebras and their relations with geometry have found natural explanations from the perspective of this twist of M-theory \cite{gaiotto2020miura}, \cite{Oh:2021wes}.
\end{itemize}

The example we consider is closely related to the second of these. \surya{more}
\iffalse
Indeed, there is an odd nilpotent element in $\mf{osp}(6|2)$, which we refer to as $S$ in the sequel. Using the inner action of $\mf{osp}(6|2)$ on our eleven-dimensional model on twisted $AdS_7\times S^4$ as identified in proposition \ref{prop:brads7}, $S$ affords a deformation of our model. This is the deformation considered in \cite{BeemEtAl}, and it induces a specialization of characters called the Schur limit.
\fi

\subsection{M5 branes, holomorphy, and holography}
Let us begin by spelling out the objects in expectation \ref{twistedholog} adapted to our setting.

\begin{itemize}
\item The 11d spacetime manifold $X$ is $\R\times \C^5$ and $Y$ is a copy of $\C^3$. 
\item The factorization algebra $\Obs_{grav}|_{\C^3}$ has the feature that its semiclassical free limit is the factorization algebra denoted $\clie ^\bullet \left ( \Pi \Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4})\right )$ in definition \ref{defn:ads7states}.
\item The factorization algebra $\Obs^N_{CFT}$ describes local observables in the minimal twist of the theory on a stack of $N$ M5 branes wrapping $\C^3$. 
\end{itemize}

Our goal is to try and use this map, and expectations about its kernel and cokernel, to give a concrete description of the target. There have been various approaches to try and characterize the spectrum of $\frac{1}{16}$-BPS states in the 6d $\mc N=(2,0)$ theories of type $A_{N-1}$, which furnish consistency checks to test our proposal against. Some of these involve applications of instanton counting techniques in 5d $\mc N=2$ gauge theory \cite{Kim:2013nva} and some of them involve holographic techniques \cite{Imamura}.

As we remarked in subsection \ref{bpsadscft}, the first ingredient is a map of representations of the superconformal algebra between local operators of the CFT and supergravity states. In order to codify such a matching in terms of the kinds of data in the statement of expectation \ref{twistedholog}, we require a matching between supergravity states and the costalk at the origin of the factorization algebra $(\Obs_{grav}|_{\C^3})^!$.

\surya{need to add minimal recollections from graviton paper}
\parsec[]

We have the following conjectural large $N$ statements

\begin{conj}[R-Saberi-Williams]\label{conj:classical}
There is an equivalence of holomorphic $\mb{P}_0$-factorization algebras \[ \left( \clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a twisted factorization envelope of the local $L_\infty$-algebra $\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$. Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to a twisted factorization envelope of the local Lie algebra $\operatorname {Diff}_{\C}$ of holomorphic differential operators on $\C$. 
\end{conj}

Here, the twisting cocycle $\omega$ comes from the shifted Poisson tensor that was induced by the flux in section \ref{sec:ads}. The content in verifying this conjecture is to explicitly compute the twisting coming from the flux sourced by the brane, and check that upon deforming by the element $S$, it induces the correct cocycle on $\operatorname{Diff}(\C^\times)$

The comment in \ref{eqn:winfty} constitutes a very meager consistency check for the second part of this conjecture, where we observe that the Schur limit of the character of the costalk of $\mc U_{\omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} ) \right)$ recovers the vacuum character of the $W_{1+\infty}$ vertex algebra.

There is a deformation of the twisted factorization envelope of $\operatorname{Diff}_\C$ which yields the $\mc W_{1+\infty}$ vertex algebra, also referred to as the affine Yangian of $\mf {gl}(1)$. In \cite{CostelloM5}, Costello finds this deformation from a loop level computation in his 5d noncommutative gauge theory. We also expect to be able to lift this to the minimal twist. We summarize this expectation in a conjecture.

\begin{conj}[R-Saberi-Williams]
There is an equivalence of holomorphic factorization algebras \[ \left( \clie^\bullet_\hbar (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^!\cong \mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right ).\] where the right hand side denotes a deformation of the factorization algebra in the previous conjecture induced by loop-level effects in our eleven-dimensional model. Moreover, upon deforming by the Maurer-Cartan element $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_{\hbar, \omega} \left ( \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )\right )$ has no sections away from a copy of $\C\subset \C^3$, and its restriction to this copy of $\C$ is equivalent to the $\mc {W}_{1+\infty}$ vertex algebra.
\end{conj}

\parsec[]
We now move on to finite $N$ statements. For the lowest steps of the filtration, we can make some very concrete statements.

\begin{conj}[R-Saberi-Williams]
Upon deforming by $S\in \mf {osp}(6|2)$, the factorization algebra $\mc U_\omega (\mc G^{(-1)}_{\C^3} )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Heisenberg vertex algebra.
\end{conj}
To check this conjecture, it remains to compute the pullback of the twisting cocycle $\omega$ under the inclusion of $\mc G^{(0)}$ and see that it deforms to the Heisenberg cocycle.

\parsec[]
There is a distinguished Lie sub-algebra of the algebra of differential operators on $\C^\times$ which is given by the Witt-algebra of vector fields. The central extension of $\operatorname{Diff} (\C^\times)$ induced by $\omega$ above restricts to the Virasoro central extension. Similarly, in proposition \ref{prop:g0e36} we have identified a distinguished local super-Lie algebra inside $\Pi\Omega^{0,\bullet} _{\C^3}(\mc L^{r=0} _{AdS_7\times S^4} )$ given by $\mc E(3|6)$.

Accordingly, we conjecture the following
\begin{conj}[R-Saberi-Williams]
Upon deforming by $S\in \mf{osp}(6|2)$, the factorization algebra $\mc U_\omega( \mc E(3|6) )$ has no sections away from a copy of $\C\subset \C^3$ and its restriction to this copy of $\C$ is equivalent to the Virasoro vertex algebra.
\end{conj}

Again, to check this conjecture it remains to compute the pullback of the twisting cocycle $\omega$ along the inclusion $\mc E(3|6)\to \Pi\Omega^{0,\bullet}_{\C^3} (\mc L^{r=0}_{AdS_7\times S^4} )$ and compare its deformation with the cocycle giving the Virasoro central extension.

We can once again perform a consistency check at the level of characters of costalks. Indeed, we see that the plethystic exponential of the specialized character $g_0(y=1, y_3=1, q) = \frac{q^2}{1-q}$ is exactly the vacuum character of the Virasoro algebra.

Moreover, note that combining with conjecture \ref{conj:classical}, we expect maps 
\[\mc U_\omega( \mc E(3|6) )\to \left (\clie^\bullet (\Pi\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))\right)^! \to \Obs^N_{CFT}\] for every $N$. This map can be thought of as a Noether-type map associated to an  $\mc E(3|6)$-symmetry of the minimal twist of any finite rank 6d $\mc N=(2,0)$ theory \cite{CG2}.

\parsec[]
More generally, the $\mc W_{1+\infty}$ algebra has as quotients, the $\mc W_N$ algebras when the central charge is set equal to $N$. Accordingly, we dream of the following:

\begin{spec}
Under an integrality condition on the central charge, the map \[ (\Obs_{grav} |_{\C^3} )^! \to \Obs^N_{CFT}\] factors as
\[
\begin{tikzcd}
(\Obs_{grav} |_{\C^3} )^! \ar[r]\ar[d]  & \Obs^N_{CFT} \\
\mc U_{\hbar, \omega} (\Omega^{0,\bullet}_{\C^3} (\mc L^N_{AdS_7\times S^4}))/\mc U_{\hbar, \omega} (\prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3} ) \ar[ur]
\end{tikzcd}
\]
\end{spec}

We can perform a consistency check of the above speculation at the level of characters of costalks. It is expected that the superconformal deformation deforms $\Obs^N_{CFT}$ to the $\mc{W}_N$ vertex algebra. On the other hand, we have that

\begin{prop}
Upon specializing $y=1,y_3=1$ (so that $y_1 y_2 = 1$), one has

\begin{align*}
\chi \left ( \Omega^{0,\bullet}_{\C^3,c} (\mc L^N_{AdS_7\times S^4})(0)/ \left ( \mc G^{(-1)}_{\C^3,c}\times \prod _{j\geq {N-1}} \mc G^{(j)}_{\C^3,c}\right )(0)\right ) & = \sum_{j \geq 0}^{N-2} g_j (y_1,y_2, y_3=1,y=1,q) \\
& = \frac{q^2 + q^3 + \cdots + q^{N}}{1-q} 
\end{align*}

The plethystic exponential of the right hand side agrees with the vacuum character of the $W_{N}$ vertex algebra.
\end{prop}
\begin{proof}
By induction it suffices to show that the specialization of the single particle local character $g_j$ of the factorization algebra $\mc U(\mc{G}_{\C^3}^{(j)})$ is $q^{j+2} / (1-q)$. 
We have already seen this in the case $j=-1,0$, so it suffices to show this when $k \geq 1$.

First observe that the denominator becomes
\begin{equation}
(1-y_1 q)(1-y_2q) (1-q) .
\end{equation}

Next, we observe that the numerator of $g_j (y_1,y_2,y_3=1,y=1,q)$ can be factored as
\begin{align*}
q^{3 + 3j/2} \left(q^{-(j+2)/2} + q^{-(j-2)/2} - q^{-j/2} (y_1+y_2) \right) 
& = q^{j+2} (1 + q^2 - q (y_1 + y_2)) \\
& = q^{j+2} (1 - y_1 q) (1-y_2 q) 
\end{align*}
where in the last line we have used $y_1 y_2 = 1$.
The result follows.
\end{proof}

\parsec{}
In this article, we analyze the discrepancy between the characters of $\mc U (\mc G^{(j)}_{\C^3})$ and expectations about the superconformal index of the finite rank 6d $\mc N=(2,0)$ theories computed via instanton counting techniques \cite{Kim:2013nva} and the "giant graviton expansion" \cite{Arai_2020, Imamura}. We propose that the discrepancies can be categorified by modules for $E(3|6)$.

\surya{haven't edited below}
\subsection{Infinite dimensional symmetry enhancement by exceptional simple super Lie algebras}
